Memory-Efficient Mixed-Precision Implementations\\for Robust Explicit Model Predictive Control

### 2019-04-12 emsoft-2019/experiments.tex
fix for experiments

%The second difference consists in the last two lines in Table\ref{tab:ipd}.
For the aircraft example, when $\varepsilon_Q=0.0030$, the error due to selecting the wrong region (\maxUij) 
exceeds the given value of $\Delta=0.1$ and our algorithm
needs to design a new controller (corresponding to the \texttt{No} branch in~\autoref{fig:overview}). 
The loop converges after 5 iterations (\texttt{Yes}
branch of the diagram) with $\Delta=0.112$. In each iteration, the value
for $\Delta$ is increased by $\varepsilon_{SAFE} = 10^{-3}$.
Thus, the algorithm reduces memory demand
at the expense of slightly more disturbance for the controller. When
$\varepsilon_Q=0.0050$ the analysis converges after 4 iterations.
\eva{Does this mean that for the other settings, the loop in~\autoref{fig:overview}
is executed only once?}

>>>>

%The second difference consists in the last two lines in Table\ref{tab:ipd}.
For the aircraft example, when $\varepsilon_Q=0.0030$, the error due to selecting the wrong region (\maxUij) 
exceeds the given value of $\Delta=0.1$ and our algorithm
needs to design a new controller (corresponding to the \texttt{else} branch in~\autoref{lst:alg}). 
The loop converges after 5 iterations (\texttt{then}
branch in our algorithm) with $\Delta=0.112$. In each iteration, the value
for $\Delta$ is increased by $\varepsilon_{SAFE} = 10^{-3}$.
Thus, the algorithm reduces memory demand
at the expense of slightly more disturbance for the controller. When
$\varepsilon_Q=0.0050$ the analysis converges after 4 iterations.
\eva{Does this mean that for the other settings, the loop in~\autoref{fig:overview}
is executed only once?}
